### 2014-05-21 learn_intro.tex
All fixes through 2:39 p.m.

Over the full range of 1~Mbps to 1000~Mbps, the ``thousand-fold''
RemyCC protocol matched or outperformed TCP Cubic and
Cubic-over-sfqCoDel over the entire range
(Figure~\ref{fig:breadth}). This result suggests that it may be
possible to construct ``one size fits all'' end-to-end
congestion-control protocols that outperform TCP, even when TCP is
assisted by in-network algorithms.

>>>>

Over the full range of 1~Mbps to 1000~Mbps, the ``thousand-fold''
RemyCC protocol matched or outperformed TCP Cubic and
Cubic-over-sfqCoDel at every link rate
(Figure~\ref{fig:breadth}). This result suggests that it may be
possible to construct ``one size fits all'' end-to-end
congestion-control protocols that outperform TCP, even when TCP is
assisted by in-network algorithms.

### 2014-05-21 sprout_contest.tex
All fixes through 2:39 p.m.

Forty students participated in the contest. At the outset, we gave
students a ``training'' trace from the Verizon LTE network and
Sprout's source code, and set up a dynamic leaderboard that showed the
best performance of every other student thus far, as well as results
from Skype and Sprout.\footnote{We also provided students with a
  second training trace to evaluate the robustness of their candidate
  algorithms.} During the course of the contest, the students made
almost 3,000 attempts to maximize power over the Verizon trace.

>>>>

Forty students participated in the contest. At the outset, we gave
students a ``training'' trace from the Verizon LTE network and
Sprout's source code, and set up a dynamic leaderboard that showed the
best performance of every student thus far, as well as results
from Skype and Sprout.\footnote{We also provided students with a
  second training trace to evaluate the robustness of their candidate
  algorithms.} During the course of the contest, the students made
almost 3,000 attempts to maximize power over the Verizon trace.

### 2014-05-21 sprout_related.tex
All fixes through 2:39 p.m.

Google has proposed a congestion-control scheme~\cite{WebRTCdraft} for
the WebRTC system that uses an arrival-time filter at the receiver,
along with other congestion signals, to decide whether a real-time
flow should increase, decrease, or hold its current bit rate. We plan
to investigate this system and assess it on the same metrics as the
other schemes in our evaluation.

>>>>

Google has proposed a congestion-control scheme~\cite{WebRTCdraft} for
the WebRTC system that uses an arrival-time filter at the receiver,
along with other congestion signals, to decide whether a real-time
flow should increase, decrease, or hold its current bit rate.% We plan
%to investigate this system and assess it on the same metrics as the
%other schemes in our evaluation.

### 2014-05-21 sprout_sprout.tex
All fixes through 2:39 p.m.

Figure~\ref{f:vzinter} illustrates the {\em interarrival} distribution
of 1.2 million MTU-sized packets received at a stationary cell phone
whose downlink was saturated with these packets. For the vast majority
of packet arrivals (the 99.99\% that come within 20~ms of the previous
packet), the distribution fits closely to a memoryless point process,
or Poisson process, but with fat tails suggesting the impact of
channel quality-dependent scheduling, the effect of other users, and
channel outages, that yield interarrival times between 20 ms and as
long as four seconds.  Such a ``switched'' Poisson process produces a
$1/f$ distribution, or {\em flicker noise}. The best fit is shown in
the plot.\footnote{We can't say exactly why the distribution should
  have this shape, but physical processes could produce such a
  distribution. Cell phones experience fading, or random variation of
  their channel quality with time, and cell towers attempt to send
  packets when a phone is at the apex of its channel quality compared
  with a longer-term average. }
%\anirudh{TWhat is the -3.27 in the exponent of t ? Maybe a desc of flicker noise would help ?}

>>>>

Figure~\ref{f:vzinter} illustrates the {\em interarrival} distribution
of 1.2 million MTU-sized packets received at a stationary cell phone
whose downlink was saturated with these packets. For the vast majority
of packet arrivals (the 99.99\% that come within 20~ms of the previous
packet), the distribution fits closely to a memoryless point process,
or Poisson process, but with fat tails suggesting the impact of
channel-quality-dependent scheduling, the effect of other users, and
channel outages, that yield interarrival times between 20 ms and
almost four seconds.  Such a ``switched'' Poisson process produces a
$1/f$ distribution, or {\em flicker noise}. The best fit is shown in
the plot.\footnote{We can't say exactly why the distribution should
  have this shape, but physical processes could produce such a
  distribution. Cell phones experience fading, or random variation of
  their channel quality with time, and cell towers attempt to send
  packets when a phone is at the apex of its channel quality compared
  with a longer-term average. }
%\anirudh{TWhat is the -3.27 in the exponent of t ? Maybe a desc of flicker noise would help ?}
